### 2015-08-06 evaluation.tex
Added a blurb how SMACK is now more sound

\noindent\textbf{Experimental Setup }
%
We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5, Z3~4.3.2, Boogie rev. 4192 and \corral rev. 534. We also used Mono~4.1.0 to run Boogie and \corral.

>>>>

\noindent\textbf{Experimental Setup }
%
We performed all experiments on a 3.40GHz Intel Core i7-2600 CPU with 16GB RAM running Ubuntu Linux 12.04.5 LTS, LLVM 3.5, SMACK 1.5.0, Z3~4.3.2, Boogie rev. 4192 and \corral rev. 534. We also used Mono~4.1.0 to run Boogie and \corral.

### 2015-08-06 whoop.tex
Added a blurb how SMACK is now more sound

In addition to inheriting soundness issues arising from currently unknown bugs in \whoop and in the external tools that \whoop relies on, we acknowledge that: (i) SMACK is subject to sources of unsoundness, e.g.\ it models integers as an infinite set (rather than as a finite set of bit-vectors), and its memory model can potentially be unsound in (typically rare) situations where programs use unaligned byte-level memory accesses; and (ii) that the combination of Clang and SMACK commits our approach to specific choices related to undefined and implementation-defined aspects of the C language when translating to Boogie.  However, \whoop makes no fundamental assumptions related to these translation decisions, meaning that a more accurate C-to-Boogie translation would automatically lead to a more accurate analysis with \whoop.

>>>>

In addition to inheriting soundness issues arising from currently unknown bugs in \whoop and in the external tools that \whoop relies on, we acknowledge that: (i) the 1.5.0 release of SMACK we used is subject to sources of unsoundness, e.g.\ it models integers as an infinite set (rather than as a finite set of bit-vectors), and its memory model can potentially be unsound in (typically rare) situations where programs use unaligned byte-level memory accesses;\footnote{Note that currently bit-vectors and unaligned byte-level memory accesses are soundly and precisely handled by SMACK (as of release 1.5.1).} and (ii) that the combination of Clang and SMACK commits our approach to specific choices related to undefined and implementation-defined aspects of the C language when translating to Boogie.  However, \whoop makes no fundamental assumptions related to these translation decisions, meaning that a more accurate C-to-Boogie translation would automatically lead to a more accurate analysis with \whoop.
